Final Project Code ALL

### 2022-12-11 Draft_Final_Code.Rmd
Added titles to plots

gam_mod1 %>% pluck('fit') %>% plot()
```

@@

ggplot(imdb_clean, aes(x = Budget, y = Gross)) + 
  geom_point() + 
  labs(x = "Budget in USD", 
       y = "Gross Profit in USD (Log Scale)", 
       title = "Preliminary Visualizations") +
  theme_classic()

>>>>

gam_mod1 %>% pluck('fit') %>% plot(main = "Non-Linear Visualizations")
```

@@

imdb_clean %>%
  filter(Budget > 1) %>% 
  ggplot(aes(x = Budget, y = Gross)) + 
  geom_point() + 
  labs(x = "Budget in USD", 
       y = "Gross Profit in USD (Log Scale)", 
       title = "Preliminary Visualizations") +
  theme_classic()
